Taking uncertainty in word embedding bias estimation seriously: a bayesian approach

### 2022-07-25 paperDraft/paperDraft4.Rmd
Updates paper structure
small structure changes

\raf{fix bibliography}

\ali{proofread and think if we should add more}

@@

@@

# Non-statistical problems with cosine-based measures of bias

@@

# Statistical issues

@@

>>>>

## Word embeddings and their bias

- akapit filozoficzny, z odniesieniem do value free

@@

- undesirable bias with respect to a certain groups words if stereotypically connected words (for stereotypes that we don't want to be used or relied on in downstream tasks) are systematically closer to each other. + EXAMPLE

## Semantical interpretation

## General challenges

## WEAT and MAC measures

@@

## Non-statistical problems with cosine-based measures of bias

@@

## Statistical issues

@@

# Pre-averaging and manufactured certainty

## General problem with pre-averaging

## Simulations for WEAT

## Simulations for MAC

# Bayesian method

## Bernstein approach

## Chasing metrics

## Bayesian method introduction

## Existing applications to NLP and perhaps to bias

## Model

# Results

## WEAT

## MAC

# Discussion and summary

# APPENDIX

## Examples of WEAT and MAC calculations

## Word lists

### 2022-07-25 paperDraft/paperDraft4.tex
small structure changes

\raf{fix bibliography}

\ali{proofread and think if we should add more}

@@

@@

>>>>

\hypertarget{word-embeddings-and-their-bias}{%
\subsection{Word embeddings and their
bias}\label{word-embeddings-and-their-bias}}

\begin{itemize}
\tightlist
\item
  akapit filozoficzny, z odniesieniem do value free
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  undesirable bias with respect to a certain groups words if
  stereotypically connected words (for stereotypes that we don't want to
  be used or relied on in downstream tasks) are systematically closer to
  each other. + EXAMPLE
\end{itemize}

\hypertarget{semantical-interpretation}{%
\subsection{Semantical interpretation}\label{semantical-interpretation}}

\hypertarget{general-challenges}{%
\subsection{General challenges}\label{general-challenges}}

\hypertarget{weat-and-mac-measures}{%
\subsection{WEAT and MAC measures}\label{weat-and-mac-measures}}

@@

\hypertarget{pre-averaging-and-manufactured-certainty}{%
\section{Pre-averaging and manufactured
certainty}\label{pre-averaging-and-manufactured-certainty}}

\hypertarget{general-problem-with-pre-averaging}{%
\subsection{General problem with
pre-averaging}\label{general-problem-with-pre-averaging}}

\hypertarget{simulations-for-weat}{%
\subsection{Simulations for WEAT}\label{simulations-for-weat}}

\hypertarget{simulations-for-mac}{%
\subsection{Simulations for MAC}\label{simulations-for-mac}}

\hypertarget{bayesian-method}{%
\section{Bayesian method}\label{bayesian-method}}

\hypertarget{bernstein-approach}{%
\subsection{Bernstein approach}\label{bernstein-approach}}

\hypertarget{chasing-metrics}{%
\subsection{Chasing metrics}\label{chasing-metrics}}

\hypertarget{bayesian-method-introduction}{%
\subsection{Bayesian method
introduction}\label{bayesian-method-introduction}}

\hypertarget{existing-applications-to-nlp-and-perhaps-to-bias}{%
\subsection{Existing applications to NLP and perhaps to
bias}\label{existing-applications-to-nlp-and-perhaps-to-bias}}

\hypertarget{model}{%
\subsection{Model}\label{model}}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{weat}{%
\subsection{WEAT}\label{weat}}

\hypertarget{mac}{%
\subsection{MAC}\label{mac}}

\hypertarget{discussion-and-summary}{%
\section{Discussion and summary}\label{discussion-and-summary}}

\hypertarget{appendix}{%
\section{APPENDIX}\label{appendix}}

\hypertarget{examples-of-weat-and-mac-calculations}{%
\subsection{Examples of WEAT and MAC
calculations}\label{examples-of-weat-and-mac-calculations}}

\hypertarget{word-lists}{%
\subsection*{Word lists}\label{word-lists}}
\addcontentsline{toc}{subsection}{Word lists}
